---
title: "Practical 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(mosaic)
knitr::opts_chunk$set(echo = FALSE)
diet_dat <- read.csv("www/Chick_Diet.csv")
growth_dat <- read.csv("www/Chick_growth.csv")

```


# Practical 1 {.unlisted .unnumbered}
Interactive web-based environment
If for some reason you have not been able to install R/RStudio or the mosaic package on your PC, or are unable to use the Windows Virtual Desktop, you can do Practical 1 in this website.

Enter your R commands in the box below and click "Run code" when ready. **Note** This website does **not** save your R commands in a script, as is possible with RStudio. Therefore you should also open either Notepad (Windows) or TextEdit (Macs) and copy and paste your commands into the website.

The first few lines are written out for you to get started. **Note** the commands:

`library(mosaic) # can also use library(bio2020)`

`diet_dat <- read.csv("Data/Chick_Diet.csv")`

`growth_dat <- read.csv("Data/Chick_growth.csv")`


have already been run for you, so the data needed for Practical 1 and the relevant mosaic library is ready.


```{r practical_1, exercise=TRUE, exercise.lines=30}
# Introduction to R. Basic data handling

# Display the first few lines of the data
head(diet_dat)
# Inspect the structure of the data
str(diet_dat)
# Try the nrow(), ncol() and summary() functions

# Some simple summary statistics
mean(weight~Diet, data = diet_dat) 
sd(weight~Diet, data = diet_dat) 


```

